Peer-to-Peer 6502 Cellular Automata

### 2018-07-03 paper.tex
period

On termination, the transient address ranges in the memory map
(including the stack) are discarded.
If execution was terminated by timeout, then the rest of memory is also discarded,
and the state of the CA is restored
Otherwise, if the program exited (by software interrupt or undefined opcode) before timing out,
the neighborhood memory-mapped pages (zero page and other pages in the range \hexrange{4000}{7FFF}, see Table~\ref{tab:MooreNeighborhood})
are copied back to the cellular automata storage.

>>>>

On termination, the transient address ranges in the memory map
(including the stack) are discarded.
If execution was terminated by timeout, then the rest of memory is also discarded,
and the state of the CA is restored.
Otherwise, if the program exited (by software interrupt or undefined opcode) before timing out,
the neighborhood memory-mapped pages (zero page and other pages in the range \hexrange{4000}{7FFF}, see Table~\ref{tab:MooreNeighborhood})
are copied back to the cellular automata storage.
